Supplementary material for: non-coding RNAs of bird genomes

### 2014-05-22 paper/supplementary-material.tex
Updated supplementary images.

 \begin{figure}[ht]
   \includegraphics[width=0.75\textwidth]{figures/figure2.pdf}
\caption{Additional homologs of some sparsely represented RNA families were
discovered using dedicated search strategies combined with highly
sensitive settings, synteny information, lineage-specific CMs and
subsequent manual inspection.}\label{fig:2}
 \end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.9\textwidth]{figures/phylo-tree.pdf}
  \caption[]{The phylogenetic relationships between the Avian species
    used in this study. This figure has been reproduced, with permission from \cite{birds:14a}.}\label{fig:15}
\end{figure}

@@

The NCBI BioProject/SRA and Study IDs for the genomes used in this study
are are listed below.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
    \hline
Species & BioProject ID & SRA ID & Study ID \\
    \hline
\multicolumn{4}{|l|}{Genomes released before}\\
\hline
\emph{Aptenodytes forsteri} & PRJNA235982 & SRA129317 & SRP035855\\
\emph{Pygoscelis adeliae} & PRJNA235983 & SRA129318 & SRP035856\\
\emph{Gallus gallus} & PRJNA13342 & SRA030184 & SRP005856\\
\emph{Taeniopygia guttata} & PRJNA17289 & SRA010067 & SRP001389\\
\emph{Meleagris gallopavo} & PRJNA42129 & Unknown & Unknown\\
\emph{Melopsittacus undulatus} & PRJEB1588 & ERA200248 & ERP002324\\
\emph{Anas platyrhynchos} & PRJNA46621 & SRA010308 & SRP001571\\
\emph{Columba livia} & PRJNA167554 & SRA054954 & SRP013894\\
\emph{Falco peregrinus} & PRJNA159791 & SRA055082 & SRP013939\\
\emph{Geospiza fortis} & PRJNA156703 & SRA051234 & SRP011940\\
\hline
\multicolumn{4}{|l|}{Outgroups}\\
\hline
\emph{Homo sapiens} & & & \\
\emph{Alligator mississippiensis} & & & \\
\emph{Chelonia mydas} & & & \\
\hline
\multicolumn{4}{|l|}{RNA-seq data}\\
\hline
\emph{Gallus gallus} & PRJNA204941 & NA & NA \\
\emph{Gallus gallus} & NA & & SRP041863 \\
\hline
    \end{tabular}
  \end{center}
  \caption{The NCBI BioProject/SRA and Study IDs for the previously
    published genomes used in this study.}
\end{table}

>>>>

 \begin{figure}[ht]
   \includegraphics[width=0.95\textwidth]{figures/figure2.pdf}
\caption{Additional homologs of some sparsely represented RNA families were
discovered using dedicated search strategies combined with highly
sensitive settings, synteny information, lineage-specific CMs and
subsequent manual inspection.}\label{fig:2}
 \end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.99\textwidth]{figures/HOTAIR_loci_expression.pdf}
\includegraphics[width=0.99\textwidth]{figures/HOTAIRM1_2.pdf}
  \caption[]{Above: Expression of the chicken HOTAIRM1 (RF01976) locus
    and the surrounding genes: HOXA1, HOXA2, and HOXA3. Below: The
    predicted secondary structure of the Avian HOTAIRM1 domain.}\label{fig:15}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.99\textwidth]{figures/HOTAIR_loci_synteny.pdf}
  \caption[]{The preservation of gene order (synteny) surrounding the
    HOTAIRM1 (RF01976) locus across the Avian and other Vertebrate
    lineages.}\label{fig:16}
\end{figure}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|r|c|}
    \hline
RNA family (Rfam ID) & Chromosome & Coordinates & Strand \\
    \hline
\multicolumn{4}{|l|}{Macro-chromosomes:}\\
RNase MRP (RF00030)     & chr4 & 39276202-39276488 & -\\
\multicolumn{4}{|l|}{Micro-chromosomes:}\\ 
U4atac snRNA (RF00618)  & chr7 &	25702714-25702831 & +\\
RNase P RNA (RF00009)   & chr8 & 6609347-6609668   & -\\
Telomerase RNA (RF00024)& chr9 & 19429028-19429084 & +\\
Vault RNA (RF00006)     & chr13& 380747-380840     & +\\
U11 snRNA (RF00548)     & chr23& 2216932-2217058   & -\\
\hline
    \end{tabular}
  \end{center}
  \caption{The location of ``missing'' RNA families in the chicken genome (galGal4). }
\end{table}

\begin{figure}[ht]
\includegraphics[width=0.9\textwidth]{figures/phylo-tree.pdf}
  \caption[]{The phylogenetic relationships between the Avian species
    used in this study. This figure has been reproduced, with permission from \cite{birds:14a}.}\label{fig:17}
\end{figure}

@@

The NCBI BioProject, SRA and Study IDs for the genomes used in this study
are are listed below.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
    \hline
Species & BioProject ID & SRA ID & Study ID \\
    \hline
\multicolumn{4}{|l|}{Genomes released before}\\
\hline
\emph{Aptenodytes forsteri} & PRJNA235982 & SRA129317 & SRP035855\\
\emph{Pygoscelis adeliae} & PRJNA235983 & SRA129318 & SRP035856\\
\emph{Gallus gallus} & PRJNA13342 & SRA030184 & SRP005856 (galGal4)\\
\emph{Taeniopygia guttata} & PRJNA17289 & SRA010067 & SRP001389\\
\emph{Meleagris gallopavo} & PRJNA42129 & Unknown & Unknown\\
\emph{Melopsittacus undulatus} & PRJEB1588 & ERA200248 & ERP002324\\
\emph{Anas platyrhynchos} & PRJNA46621 & SRA010308 & SRP001571\\
\emph{Columba livia} & PRJNA167554 & SRA054954 & SRP013894\\
\emph{Falco peregrinus} & PRJNA159791 & SRA055082 & SRP013939\\
\emph{Geospiza fortis} & PRJNA156703 & SRA051234 & SRP011940\\
\hline
\multicolumn{4}{|l|}{Outgroups}\\
\hline
\emph{Homo sapiens} & & & HG19/GRCh37\\
\emph{Alligator mississippiensis} & & & allMis1\\
\emph{Chelonia mydas} & PRJNA104937 & & \\
\hline
\multicolumn{4}{|l|}{RNA-seq data}\\
\hline
\emph{Gallus gallus} & PRJNA204941 & NA & NA \\
\emph{Gallus gallus} & NA & NA & SRP041863 \\
\hline
    \end{tabular}
  \end{center}
  \caption{The NCBI BioProject/SRA and Study IDs for the previously
    published genomes used in this study.}
\end{table}
